Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-12 paper/main.tex
Updated with graphs from latest run
Some parts to discussion

>>>>

\subsection{Faster implementations}
We do not claim to have tested the fastest possible nor existing version
of most of the candidates. We are certain that someone of more skill and
knolwedge about the inner workings of the \ac{SHA}-3 candidates, \ac{GCC} and
Python could make significantly faster implementation.

\subsection{Test with different Erasure Coding schemes}
By default Tahoe-\ac{LAFS} comes with a coding scheme of 3-7-10 (shares needed,
shares happy, shares total) while we test with a configuration of 2-3-3. It
would have been interesting to see how this (and other schemes) would affect
both the overall performance and the percentage of time spent hashing.

\subsection{Measure with real use cases}
Our test use random generated data of a certain length. In a real use case for
Tahoe-\ac{LAFS} the data would probably be both of varying length, and of
lengths not tested by us. In a real use case both a feasible erasure coding
scheme would have to be decided, and the files would represent what you
actually would want to use Tahoe-\ac{LAFS} for.
